### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@88e2dcdd5543b53a5899feea2eec4da34f7b286b 🚀

\begin{longtable}[]{@{}lll@{}}
\toprule
Method & Embedding approach & Reference\tabularnewline
\midrule
\endhead
RDPG & graphs through SVD & Young \& Scheinerman (2007)\tabularnewline
tSNE & nodes through statistical divergence & Hinton \& Roweis
(2002)\tabularnewline
DeepWalk & graph walk & Perozzi et al. (2014)\tabularnewline
FastEmbed & graph through PCA/SVD analogue & Ramasamy \& Madhow
(2015)\tabularnewline
LINE & nodes through statistical divergence & Tang et al.
(2015)\tabularnewline
SDNE & nodes through auto-encoding & D. Wang et al.
(2016)\tabularnewline
node2vec & node embedding & Grover \& Leskovec (2016)\tabularnewline
graph2vec & sub-graph embedding & Narayanan et al. (2017)\tabularnewline
HARP & nodes through a meta-strategy & Chen et al. (2017)\tabularnewline
Joint methods & multiple graphs & S. Wang et al. (2021)\tabularnewline
\bottomrule
\end{longtable}

@@

>>>>

\begin{longtable}[]{@{}llll@{}}
\toprule
Method & Embedding approach & Reference & Ecological
application\tabularnewline
\midrule
\endhead
RDPG & graphs through SVD & Young \& Scheinerman (2007) & Wardeh et al.
(2021)\tabularnewline
tSNE & nodes through statistical divergence & Hinton \& Roweis (2002)
&\tabularnewline
DeepWalk & graph walk & Perozzi et al. (2014) &\tabularnewline
FastEmbed & graph through PCA/SVD analogue & Ramasamy \& Madhow (2015)
&\tabularnewline
LINE & nodes through statistical divergence & Tang et al. (2015)
&\tabularnewline
SDNE & nodes through auto-encoding & D. Wang et al. (2016)
&\tabularnewline
node2vec & node embedding & Grover \& Leskovec (2016) &\tabularnewline
graph2vec & sub-graph embedding & Narayanan et al. (2017)
&\tabularnewline
HARP & nodes through a meta-strategy & Chen et al. (2017)
&\tabularnewline
Joint methods & multiple graphs & S. Wang et al. (2021) &\tabularnewline
\bottomrule
\end{longtable}

@@

\leavevmode\hypertarget{ref-Wardeh2021PreMam}{}%
Wardeh, M., Baylis, M., \& Blagrove, M. S. C. (2021). Predicting
mammalian hosts in which novel coronaviruses can be generated.
\emph{Nature Communications}, \emph{12}(1, 1), 780.
\url{https://doi.org/10.1038/s41467-021-21034-5}
